---
title: "dplyr_tut_1"
output: html_document
---
re carat is > 0.5

"### Example
Filter all rows 
where carat is > 0.5

### Code
```{r}
diamonds_sample %>% filter(carat > 0.5)

# Or, alternatively
filter(diamonds_sample, carat > 0.5)
```"
"### Example

Filter all rows 
where clarity is equal to VVS2

### Code

```{r}
diamonds_sample %>% filter(clarity == ""VVS2"")

# Or, alternatively
filter(diamonds_sample, clarity == ""VVS2)
```

### Comment
Note that the comparison operator is a double equal sign (a single equal sign is an assignment operator)"
"### Example
Filter all rows 
where carat is > 0.5 & clarity is equal to VVS2

### Code

```{r}
diamonds_sample %>% filter(carat > 0.5 & clarity == ""VVS2"")

# Or, alternatively
filter(diamonds_sample, carat > 0.5 & clarity == ""VVS2"")
```

### Comment

For OR conditions use the OR operator - `|`"
"### Example
Filter all rows 
where carat is > 0.5 & clarity is equal to VVS2 or SI1

### Code

```{r}
diamonds_sample %>% filter(carat > 0.5 & clarity %in% c(""VVS2"",""SI1""))

# Or, alternatively
filter(diamonds_sample, carat > 0.5 & clarity %in% c(""VVS2"",""SI1""))
```



### Comment

`%in%` operator is used for comparing multiple values"
